Unsupervised embeddings of organizations capture latent structure of scientific mobility

### 2020-04-10 paper/current/main.tex

Let $T_{ij}$ represents the total \textbf{flux}, the number of people who moved between organizations $i$ and $j$. $M_{i}$ and $M_{j}$ represent the size of an organization. According to our gravity model on the embedding space,

@@

Combining Eq.~\ref{eq:approxi_mass_term}, we have

>>>>

Let $T_{ij}$ represents the \textbf{flux}, the number of people who moved between organizations $i$ and $j$. $M_{i}$ and $M_{j}$ represent the size of an organization. According to our gravity model on the embedding space,

@@

In or model, $\#(w_i)$ and $\#(w_j)$ are total flux $M_i$ and $M_j$ respectively,  and $\#(w_i,w_j)$ is just  $T_{ij}$, flux between i and j. Then, we have same expression with gravity model,
